---
title: "Initial Analyses"
author: "Shomit Ghosh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple Analysis - MNL

In this file, I have included the code for MNL using the main variables (excluding customer heterogneity, so just competition). For each strategic goal, I have one model that runs on unbalanced data and another model that runs on a balanced dataset (using random oversampling)

Load data and packages

```{r}
load("cleaned.RData")
load("acq.RData")
load("churn.RData")
load("xsell.RData")
load("upsell.RData")
```

```{r}
library(caret)
library(nnet)
library(ggplot2)
library(dplyr)
library(randomForest)
library(glmnet)
library(plotly)
```

**1 .Acquisition - MNL (unbalanced, main)**

```{r}
# Final cleaning
acq_mnl_main_unbal <- acq[, !(names(acq) %in% c("delta_hlv", "BB_downloadSpeed_current", "BB_downloadSpeed_best", "CampaignName", "CampaignType", "StrategicGoal", "decision_date", "reward_date", "strat_new"))]

acq_mnl_main_unbal <- droplevels(acq_mnl_main_unbal)
acq_mnl_main_unbal$reaction <- relevel(acq_mnl_main_unbal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_acq_main_unbal <- createDataPartition(acq_mnl_main_unbal$reaction, p = 0.8, list = FALSE)
train_acq_mnl_main_unbal <- acq_mnl_main_unbal[train_rows_acq_main_unbal,]
test_acq_mnl_main_unbal <- acq_mnl_main_unbal[-train_rows_acq_main_unbal,]

# Model training
model_acq_mnl_main_unbal <- multinom(data = train_acq_mnl_main_unbal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_acq_mnl_main_unbal

# Model test
preds_acq_mnl_main_unbal <- predict(model_acq_mnl_main_unbal, newdata = test_acq_mnl_main_unbal)
conf_matrix_acq_mnl_main_unbal <- confusionMatrix(data = preds_acq_mnl_main_unbal, reference = test_acq_mnl_main_unbal$reaction)
conf_matrix_acq_mnl_main_unbal
```

**2. Acquisition - MNL (balanced, main)**

```{r}
# Balance data
table(acq_mnl_main_unbal$reaction)
acq_mnl_main_bal <- acq_mnl_main_unbal %>%
  group_by(reaction) %>%
  slice_sample(n = max(table(acq_mnl_main_unbal$reaction)), replace = TRUE)
table(acq_mnl_main_bal$reaction)

# Split data
set.seed(100)
train_rows_acq_main_bal <- createDataPartition(acq_mnl_main_bal$reaction, p = 0.8, list = FALSE)
train_acq_mnl_main_bal <- acq_mnl_main_bal[train_rows_acq_main_bal,]
test_acq_mnl_main_bal <- acq_mnl_main_bal[-train_rows_acq_main_bal,]

# Model training
model_acq_mnl_main_bal <- multinom(data = train_acq_mnl_main_bal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_acq_mnl_main_bal

# Model test
preds_acq_mnl_main_bal <- predict(model_acq_mnl_main_bal, newdata = test_acq_mnl_main_bal)
conf_matrix_acq_mnl_main_bal <- confusionMatrix(data = preds_acq_mnl_main_bal, reference = test_acq_mnl_main_bal$reaction)
conf_matrix_acq_mnl_main_bal
```

**3. Churn - MNL (unbalanced, main)**

```{r}
# Final cleaning
churn_mnl_main_unbal <- churn[, !(names(churn) %in% c("delta_hlv", "BB_downloadSpeed_current", "BB_downloadSpeed_best", "CampaignName", "CampaignType", "StrategicGoal", "decision_date", "reward_date", "strat_new"))]

churn_mnl_main_unbal <- droplevels(churn_mnl_main_unbal)
churn_mnl_main_unbal$reaction <- relevel(churn_mnl_main_unbal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_churn_main_unbal <- createDataPartition(churn_mnl_main_unbal$reaction, p = 0.8, list = FALSE)
train_churn_mnl_main_unbal <- churn_mnl_main_unbal[train_rows_churn_main_unbal,]
test_churn_mnl_main_unbal <- churn_mnl_main_unbal[-train_rows_churn_main_unbal,]

# Model training
model_churn_mnl_main_unbal <- multinom(data = train_churn_mnl_main_unbal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_churn_mnl_main_unbal

# Model test
preds_churn_mnl_main_unbal <- predict(model_churn_mnl_main_unbal, newdata = test_churn_mnl_main_unbal)
conf_matrix_churn_mnl_main_unbal <- confusionMatrix(data = preds_churn_mnl_main_unbal, reference = test_churn_mnl_main_unbal$reaction)
conf_matrix_churn_mnl_main_unbal
```

**4. Churn - MNL (balanced, main)**

```{r}
# Balance data
table(churn_mnl_main_unbal$reaction)
churn_mnl_main_bal <- churn_mnl_main_unbal %>%
  group_by(reaction) %>%
  slice_sample(n = max(table(churn_mnl_main_unbal$reaction)), replace = TRUE)
table(churn_mnl_main_bal$reaction)

# Split data
set.seed(100)
train_rows_churn_main_bal <- createDataPartition(churn_mnl_main_bal$reaction, p = 0.8, list = FALSE)
train_churn_mnl_main_bal <- churn_mnl_main_bal[train_rows_churn_main_bal,]
test_churn_mnl_main_bal <- churn_mnl_main_bal[-train_rows_churn_main_bal,]

# Model training
model_churn_mnl_main_bal <- multinom(data = train_churn_mnl_main_bal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_churn_mnl_main_bal

# Model test
preds_churn_mnl_main_bal <- predict(model_churn_mnl_main_bal, newdata = test_churn_mnl_main_bal)
conf_matrix_churn_mnl_main_bal <- confusionMatrix(data = preds_churn_mnl_main_bal, reference = test_churn_mnl_main_bal$reaction)
conf_matrix_churn_mnl_main_bal
```

**5. Xsell - MNL (unbalanced, main)**

```{r}
# Final cleaning
xsell_mnl_main_unbal <- xsell[, !(names(xsell) %in% c("delta_hlv", "BB_downloadSpeed_current", "BB_downloadSpeed_best", "CampaignName", "CampaignType", "StrategicGoal", "decision_date", "reward_date", "strat_new"))]

xsell_mnl_main_unbal <- droplevels(xsell_mnl_main_unbal)
xsell_mnl_main_unbal$reaction <- relevel(xsell_mnl_main_unbal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_xsell_main_unbal <- createDataPartition(xsell_mnl_main_unbal$reaction, p = 0.8, list = FALSE)
train_xsell_mnl_main_unbal <- xsell_mnl_main_unbal[train_rows_xsell_main_unbal,]
test_xsell_mnl_main_unbal <- xsell_mnl_main_unbal[-train_rows_xsell_main_unbal,]

# Model training
model_xsell_mnl_main_unbal <- multinom(data = train_churn_mnl_main_unbal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_xsell_mnl_main_unbal

# Model test
preds_xsell_mnl_main_unbal <- predict(model_xsell_mnl_main_unbal, newdata = test_xsell_mnl_main_unbal)
conf_matrix_xsell_mnl_main_unbal <- confusionMatrix(data = preds_xsell_mnl_main_unbal, reference = test_xsell_mnl_main_unbal$reaction)
conf_matrix_xsell_mnl_main_unbal
```

**6. Xsell - MNL (balanced, main)**
```{r}
# Balance data
table(xsell_mnl_main_unbal$reaction)
xsell_mnl_main_bal <- xsell_mnl_main_unbal %>%
  group_by(reaction) %>%
  slice_sample(n = max(table(xsell_mnl_main_unbal$reaction)), replace = TRUE)
table(xsell_mnl_main_bal$reaction)

xsell_mnl_main_bal <- droplevels(xsell_mnl_main_bal)
xsell_mnl_main_bal$reaction <- relevel(xsell_mnl_main_bal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_xsell_main_bal <- createDataPartition(xsell_mnl_main_bal$reaction, p = 0.8, list = FALSE)
train_xsell_mnl_main_bal <- xsell_mnl_main_bal[train_rows_xsell_main_bal,]
test_xsell_mnl_main_bal <- xsell_mnl_main_bal[-train_rows_xsell_main_bal,]

# Model training
model_xsell_mnl_main_bal <- multinom(data = train_xsell_mnl_main_bal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_xsell_mnl_main_bal

# Model test
preds_xsell_mnl_main_bal <- predict(model_xsell_mnl_main_bal, newdata = test_xsell_mnl_main_bal)
conf_matrix_xsell_mnl_main_bal <- confusionMatrix(data = preds_xsell_mnl_main_bal, reference = test_xsell_mnl_main_bal$reaction)
conf_matrix_xsell_mnl_main_bal
```

**7. Upsell - MNL (unbalanced, main)**

```{r}
# Final cleaning
upsell_mnl_main_unbal <- upsell[, !(names(upsell) %in% c("delta_hlv", "BB_downloadSpeed_current", "BB_downloadSpeed_best", "CampaignName", "CampaignType", "StrategicGoal", "decision_date", "reward_date", "strat_new"))]

upsell_mnl_main_unbal <- droplevels(upsell_mnl_main_unbal)
upsell_mnl_main_unbal$reaction <- relevel(upsell_mnl_main_unbal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_upsell_main_unbal <- createDataPartition(upsell_mnl_main_unbal$reaction, p = 0.8, list = FALSE)
train_upsell_mnl_main_unbal <- upsell_mnl_main_unbal[train_rows_upsell_main_unbal,]
test_upsell_mnl_main_unbal <- upsell_mnl_main_unbal[-train_rows_upsell_main_unbal,]

# Model training
model_upsell_mnl_main_unbal <- multinom(data = train_upsell_mnl_main_unbal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_upsell_mnl_main_unbal

# Model test
preds_upsell_mnl_main_unbal <- predict(model_upsell_mnl_main_unbal, newdata = test_upsell_mnl_main_unbal)
conf_matrix_upsell_mnl_main_unbal <- confusionMatrix(data = preds_upsell_mnl_main_unbal, reference = test_upsell_mnl_main_unbal$reaction)
conf_matrix_upsell_mnl_main_unbal
```

**8. Upsell - MNL (balanced, main)**

```{r}
# Balance data
table(upsell_mnl_main_unbal$reaction)
upsell_mnl_main_bal <- upsell_mnl_main_unbal %>%
  group_by(reaction) %>%
  slice_sample(n = max(table(upsell_mnl_main_unbal$reaction)), replace = TRUE)
table(upsell_mnl_main_bal$reaction)

upsell_mnl_main_bal <- droplevels(upsell_mnl_main_bal)
upsell_mnl_main_bal$reaction <- relevel(upsell_mnl_main_bal$reaction, ref = "No Effect")

# Split data
set.seed(100)
train_rows_upsell_main_bal <- createDataPartition(upsell_mnl_main_bal$reaction, p = 0.8, list = FALSE)
train_upsell_mnl_main_bal <- upsell_mnl_main_bal[train_rows_upsell_main_bal,]
test_upsell_mnl_main_bal <- upsell_mnl_main_bal[-train_rows_upsell_main_bal,]

# Model training
model_upsell_mnl_main_bal <- multinom(data = train_upsell_mnl_main_bal, reaction ~ mktSize_proxy + potential_mob_comp_pos + customer_presence + customer_province + month.x) # for now, interactions excluded - i.e., customer heterogeneity excluded
model_upsell_mnl_main_bal

# Model test
preds_upsell_mnl_main_bal <- predict(model_upsell_mnl_main_bal, newdata = test_upsell_mnl_main_bal)
conf_matrix_upsell_mnl_main_bal <- confusionMatrix(data = preds_upsell_mnl_main_bal, reference = test_upsell_mnl_main_bal$reaction)
conf_matrix_upsell_mnl_main_bal
```